Course Project
========================================================
The goal of the project is to predict the manner in which they did the exercise,i.e., the classe variable. 

First of all the I have done some manual preprocessing to eliminate NAs and unuseful predictors like timestamp, username, X, newwindow and numwindow as they are not the sensor measurements as such which reduced the predictors to 52
and then partitioned the data into training and testing set of 60% and 40%.

```{r}
rawData <- read.csv("pml-training.csv",na.strings=c("NA",""))
NAs <- apply(rawData,2,function(x) {sum(is.na(x))})
validData <- rawData[,which(NAs == 0)]
library(lattice)
library(ggplot2)
library(caret)
trainIndex <- createDataPartition(y = validData$classe, p=0.6,list=FALSE) 
 trainData <- validData[trainIndex,]
removeI <- grep("timestamp|X|user_name|new_window|num_window",names(trainData))
trainData <- trainData[,-removeI]
testData <- validData[-trainIndex,]
```

Once my training and test data sets are ready , now its time for training the model. Preprocessing is done with principal component analysis to reduce the dimension of predictors.

First used rpart to train the model but very low accuracy of 0.594 is detected
```{r}
library(rpart)
 modFit <- train(trainData$classe ~.,data = trainData,method="rpart")
```

Then used random forest method with cross validation of 8-fold and sample sizes of 10304 is used to achieve and accuracy of 0.966 with 100% accuracy in predicting the 20 test cases with out of sample error of 3% using confusionMatrix
```{r}
library(randomForest)
modFit <- train(trainData$classe ~.,data = trainData,method="rf", preProcess="pca", trControl = trainControl(method = "cv", number = 8), allowParallel = T)
modFit
pred = confusionMatrix(testData$classe, predict(modFit, testData))
pred
```
